Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-01 ms.tex
zorak2

@@

The X-ray luminosities of galactic nuclei provide a powerful diagnostic of the SMBH accretion rates and how they vary across different galaxy properties and SMBH masses (e.g.,  \citealt{Ho08}  and references therein).  Figure \ref{fig:vwSources} shows that the heating associated with the average star formation history of a galaxy is approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.  For a fixed wind heating parameter, the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).

This dependence is shown more directly in Figure \ref{fig:bh_growth}, where we plot the

appears to contradict the observed behavior of the nuclear X-ray luminosities of quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Gallo+10, Miller+15}.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Top panel:} Various critical values of the black hole accretion rate $\dot{M}$ in Eddington units as a function of black hole mass $M_{\bullet}$, shown separately for core ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$, dot-dashed lines).  Black lines show the accretion rate calculated from equation (\ref{eq:eddr}), according to the total stellar wind heating due to the average star formation histories from \citet{MosterNaab+:2013a} (see Appendix~\ref{app:windheat} for details).  Green lines show the maximum accretion set by Ia supernovae blow-out (\ref{eq:eddr_Ia}).  Red lines show the Compton-regulated accretion rate (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum accretion rate for a thermally stable flow near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  {\it Bottom panel:} Growth times $\Mbh/\Mdot$ in units
  of the Hubble time $\th$ for each of the accretion rates shown in the top panel.}
\end{figure}

@@

\section{Conclusions}
\label{sec:conclusions}
  We have calculated steady-state models for circumnuclear medium of a
  sample of early type galaxies, assuming that gas is supplied
  entirely by stellar wind mass loss and heated by shocked stellar
  winds and SNe Ia. We may use these profiles to calculate an $\Mdot$
  onto each of sample galaxy's SMBH, and get the scaling of $\Mdot$
  with $\Mbh$. We may then compare our results with observed trends of
  nuclear x-ray luminosity. Our main conclusions may be summarized as
  follows.

>>>>

\subsection{Black Hole Accretion Rates}

Figure \ref{fig:vwSources} shows that the heating associated with the average star formation history of a galaxy is approximately constant with SMBH mass, except for the largest black holes with $M_{\bullet} \gtrsim 5\times 10^{8}M_{\odot}$.  For a fixed wind heating parameter, the Eddington ratio $\dot{M}/\dot{M}_{\rm edd}$ increases $\propto M_{\bullet}^{0.5(0.8)}$ for core(cusp) galaxies, respectively (Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]).  Figure \ref{fig:bh_growth} displays this dependence more directly, with solid lines showing the accretion rate as calculated from equation (\ref{eq:eddr}) using the wind heating rate calculated for each black hole mass (Fig.~\ref{fig:mdot_mass}).  This average accretion rate increases from $\dot{M} \sim 10^{-6}-10^{-5}M_{\odot}$ yr$^{-1}$ for low-mass black holes ($M_{\bullet} \sim 10^{6}M_{\odot}$) to $\dot{M} \sim 10^{-4}M_{\odot}$ yr$^{-1}$ for $M_{\bullet} \sim 10^{9}M_{\sun}$.  These accretion rates fall below the maximum thermally stable accretion rate $\dot{M}_{\rm TI}$ (yellow lines), except for the highest black hole masses $\sim 10^{9}M_{\odot}$, for which the average older stellar population supplies insufficient stellar wind heating while Ia supernovae are too rare near the stagnation radius to provide effective heating.

@@

The X-ray luminosities of galactic nuclei provide a powerful diagnostic of the SMBH accretion rates and how they vary across different galaxy properties and SMBH masses (e.g.,  \citealt{Ho08}  and references therein). 
appears to contradict the observed behavior of the nuclear X-ray luminosities of quiescent galaxies, which (though showing several orders of magnitude scatter) instead on average obey $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$, where $\alpha \in [-0.4,-0.2]$ \citep{Zhang+09, Pellegrini10, Gallo+10, Miller+15}.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Top panel:} Critical values of the black hole accretion rate $\dot{M}$ in Eddington units as a function of black hole mass $M_{\bullet}$, shown separately for core ($\Gamma=0.1$, solid lines) and cusp galaxies ($\Gamma=0.8$, dot-dashed lines).  Black lines show the accretion rate calculated from equation (\ref{eq:eddr_analytic}) using the stellar wind calculated for the average star formation histories for each galaxy mass (Fig.~\ref{fig:vwSources}).  Green lines show the maximum accretion set by Ia supernovae blow-out (\ref{eq:eddr_Ia}).  Red lines show the Compton-regulated accretion rate (eq.~[\ref{eq:MdotC}]).  Yellow lines show the maximum accretion rate for a thermally stable flow near the stagnation radius (eq.~[\ref{eq:Mdotmax}]).  {\it Bottom panel:} Growth times $\Mbh/\Mdot$ in units
  of the Hubble time $\th$ for each of the accretion rates shown in the top panel.}
\end{figure}

@@

\section{Conclusions}
\label{sec:conclusions}

Apologies: we assume that average star formation histories correspond to those experienced in the nuclear region.

  We have calculated steady-state models for circumnuclear medium of a
  sample of early type galaxies, assuming that gas is supplied
  entirely by stellar wind mass loss and heated by shocked stellar
  winds and SNe Ia. We may use these profiles to calculate an $\Mdot$
  onto each of sample galaxy's SMBH, and get the scaling of $\Mdot$
  with $\Mbh$. We may then compare our results with observed trends of
  nuclear x-ray luminosity. Our main conclusions may be summarized as
  follows.
